---
title: "Lab 3"
author: "Felix Baez-Santiago"
date: "3/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Imports
```{r}
library(dplyr)
library(ggplot2)
df <- readxl::read_xls("./GSS.xls")
head(df)
names(df)


df <- df %>%
  rename(gss = `Gss year for this respondent`, happy = `General happiness`, party = `Political party affiliation`, sex = `Respondents sex`, educ = `Highest year of school completed`, divorce = `Ever been divorced or separated`, marital_status = `Marital status`, employ = `Labor force status`, id = `Respondent id number`, ballot = `Ballot used for interview`, )
df$highestSchool = as.numeric(as.character(df$educ))
```

#Question 1.
#Find the average years of education for the respondents with each marital status. Arrange your output in a meaningful order and print. Describe any patterns you find.
```{r}
df %>%
  mutate(avg_educ = as.numeric(educ)) %>%
  na.omit %>% 
  group_by(marital_status) %>%
  summarize(mean(avg_educ)
  )

head(df)
```

#Question 2.
#Create a single data frame containing records for the better educated respondents with each marital status. A “better educated” respondent is someone who has strictly more years of education than the average among those with the same marital status. Print the structure of the data frame.

```{r}
ques2 <- df %>%
  mutate(avg_school_completed = as.numeric(educ)) %>%
  na.omit %>% 
  group_by(marital_status) %>%
  summarize(betterEduc = (educ > avg_school_completed))
str(ques2)

names(df)
```


#Question 3.
#How is the happiness of a respondent related to his/her marriage status? Define that a person is happy if the response to question is “Very happy” or “Pretty happy”.

```{r}

```

#Question 4.
#Does party affiliation affect the relationship you found in the last question?
```{r}


```
#Question 5.
#How is marital status related to the education of a respondent? What are possible reasons accounting for the patterns you see?
```{r}
ggplot(df, aes(x = party, y = highestSchool)) + geom_boxplot() + theme(axis.text.x = element_text(angle = 90))
```
#Question 6.
#Explore two more interesting questions, and answer those questions using the GSS data.
```{r}
ggplot(df, aes(x=sex, fill=happy))+geom_bar(position='fill')
```

Males and females reported very similar levels of happiness.

```{r}
ggplot(df, aes(x=sex, y=highestSchool))+geom_boxplot()
names(df)
```

Females and Males have similar mean for their highest level of education, but males have a higher third quartile than females.
```
