---
title: "Lab 3"
author: "Felix Baez-Santiago"
date: "3/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Imports
```{r}
library(dplyr)
library(ggplot2)
```

#Question 1.
#Find the average years of education for the respondents with each marital status. Arrange your output in a meaningful order and print. Describe any patterns you find.
```{r}

```

#Question 2.
#Create a single data frame containing records for the better educated respondents with each marital status. A “better educated” respondent is someone who has strictly more years of education than the average among those with the same marital status. Print the structure of the data frame.

```{r}


```


#Question 3.
#How is the happiness of a respondent related to his/her marriage status? Define that a person is happy if the response to question is “Very happy” or “Pretty happy”.

```{r}




```

#Question 4.
#Does party affiliation affect the relationship you found in the last question?


#Question 5.
#How is marrital status related to the education of a respondent? What are possible reasons accounting for the patterns you see?


#Question 6.
#Explore two more interesting questions, and answer those questions using the GSS data.
