---
title: "ds202_lab3"
author: "Chris Anderson"
date: "3/4/2021"
output: html_document
---

library(dplyr)
library(ggplot2)
```{r}

dat <- readxl::read_xls('/Users/ccand/Documents/ds202_HW/Lab3/GSS.xls')
```

#Question 1.
#Find the average years of education for the respondents with each marital status. Arrange your output in a meaningful order and print. Describe any patterns you find.
```{r}
library(dplyr)

data <- filter(dat, eduYears != "No answer" & eduYears != "Don't know")

years <- as.numeric(data$eduYears)

data %>%
  group_by(Marital_status) %>%
    summarize(
      year_avg = mean(years))
```

#Question 2.
#Create a single data frame containing records for the better educated respondents with each marital status. A “better educated” respondent is someone who has strictly more years of education than the average among those with the same marital status. Print the structure of the data frame.

```{r}


```


#Question 3.
#How is the happiness of a respondent related to his/her marriage status? Define that a person is happy if the response to question is “Very happy” or “Pretty happy”.

```{r}
library(ggplot2)
happy <- filter(dat, happiness == "Pretty happy" | happiness == "Very happy")
unhappy <- filter(dat, happiness == "Not too happy")

#Respondents that responded Happy
ggplot(happy, aes(x = Marital_status)) + geom_histogram(stat="count")




```

#Question 4.
#Does party affiliation affect the relationship you found in the last question?


#Question 5.
#How is marrital status related to the education of a respondent? What are possible reasons accounting for the patterns you see?


#Question 6.
#Explore two more interesting questions, and answer those questions using the GSS data.
