---
title: "Team Report"
author: "Felix Baez-Santiago, Chris Anderson, Austin Nebel"
date: "3/5/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Imports
```{r}
library(dplyr)
library(ggplot2)
df <- readxl::read_xls("./GSS.xls")
head(df)
names(df)
```

# Question 1.
Find the average years of education for the respondents with each marital status. Arrange your output in a meaningful order and print. Describe any patterns you find.
```{r}
data <- filter(df, eduYears != "No answer" & eduYears != "Don't know")

years <- as.numeric(data$eduYears)

data %>%
  group_by(Marital_status) %>%
    summarize(
      year_avg = mean(years))
```

# Question 2.
Create a single data frame containing records for the better educated respondents with each marital status. A “better educated” respondent is someone who has strictly more years of education than the average among those with the same marital status. Print the structure of the data frame.

```{r}


```


# Question 3.
How is the happiness of a respondent related to his/her marriage status? Define that a person is happy if the response to question is “Very happy” or “Pretty happy”.

```{r}
happy <- filter(df, happiness == "Pretty happy" | happiness == "Very happy")
unhappy <- filter(df, happiness == "Not too happy")

#Respondents that responded Happy
ggplot(happy, aes(x = Marital_status)) + geom_histogram(stat="count")
ggplot(unhappy, aes(x = Marital_status)) + geom_histogram(stat="count")


```

# Question 4.
Does party affiliation affect the relationship you found in the last question?
```{r}


```
# Question 5.
How is marrital status related to the education of a respondent? What are possible reasons accounting for the patterns you see?
```{r}


```
# Question 6.
Explore two more interesting questions, and answer those questions using the GSS data.
```{r}


```
