---
title: "Team Report"
author: "Felix Baez-Santiago, Chris Anderson, Austin Nebel"
date: "3/5/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Imports
```{r}
library(dplyr)
library(ggplot2)
df <- readxl::read_xls("./GSS.xls")
head(df)
names(df)
df$highestSchool = as.numeric(as.character(df$eduYears))
```

# Question 1.
Find the average years of education for the respondents with each marital status. Arrange your output in a meaningful order and print. Describe any patterns you find.
```{r}
data <- filter(df, eduYears != "No answer" & eduYears != "Don't know")

years <- as.numeric(data$eduYears)

data %>%
  group_by(Marital_status) %>%
    summarize(
      year_avg = mean(years))
```

# Question 2.
Create a single data frame containing records for the better educated respondents with each marital status. A “better educated” respondent is someone who has strictly more years of education than the average among those with the same marital status. Print the structure of the data frame.

```{r}
ques2 <- df %>%
  mutate(avg_school_completed = as.numeric(eduYears)) %>%
  na.omit %>% 
  group_by(Marital_status) %>%
  summarize(betterEduc = (eduYears > avg_school_completed))
str(ques2)
```


# Question 3.
How is the happiness of a respondent related to his/her marriage status? Define that a person is happy if the response to question is “Very happy” or “Pretty happy”.

```{r}
happy <- filter(df, (happiness == "Pretty happy" | happiness == "Very happy" | happiness == "Not too happy") & Marital_status != "No answer")

ggplot(happy, aes(x = Marital_status, fill=happiness)) + geom_histogram(stat="count", position=position_dodge()) + ggtitle('Happiness of People per Marital Status')
ggplot(happy, aes(x = Marital_status)) + geom_histogram(stat="count", position=position_dodge()) + ggtitle('Amounts of Each Marital Status')
```

There are more married people than all other groups. Every group's "Pretty happy" rating is higher than their "very happy" rating which is interesting. Separated people have the larges proportion of "Not too happy" compared to others.

# Question 4.
Does party affiliation affect the relationship you found in the last question?
```{r}
mp <- df[,c("Marital_status","party")]

happy <- filter(df, happiness == "Pretty happy" | happiness == "Very happy") 
unhappy <- filter(df, happiness == "Not too happy")

#Respondents that responded Happy
ggplot(happy, aes(x = Marital_status, fill=party)) + geom_histogram(stat="count", position=position_dodge()) + ggtitle('Happy People') + ylim(0,6000)
ggplot(unhappy, aes(x = Marital_status, fill=party)) + geom_histogram(stat="count", position=position_dodge()) + ggtitle('Unhappy People') + ylim(0,6000)
```

# Question 5.
How is marital status related to the education of a respondent? What are possible reasons accounting for the patterns you see?
```{r}
ms_to_years <- df[,c("Marital_status","eduYears")]
ms_to_years <- filter(ms_to_years, eduYears != "No answer" & eduYears != "Don't know")
ms_to_years <- filter(ms_to_years, Marital_status != "No answer")
ms_to_years$eduYears <- as.numeric(ms_to_years$eduYears)
head(ms_to_years)
ggplot(ms_to_years, aes(x=Marital_status,y=eduYears)) + geom_boxplot()
ggplot(ms_to_years, aes(x=Marital_status)) + geom_histogram(stat="count")
```

I noticed that 'divorced' and 'never married' had the highest averages; this could be because they have more time to themselves and therefore more time to pursue education.

# Question 6.
Explore two more interesting questions, and answer those questions using the GSS data.
Question 1: Both genders reported similar levels of happiness. 
```{r}
ggplot(df, aes(x=Sex, fill=happiness))+geom_bar(position='fill')
```
Question 2: Both genders have a similar average for highest level of education, but men seem to have a larger range of values.
```{r}
ggplot(df, aes(x=Sex, y=highestSchool))+geom_boxplot()
```